Hydra Battles and Cie

### 2021-09-04 doc/part-hydras.tex
corrections chap6

\subsection{Example}

For instance the interval $[6,70]$ leads $\omega^2$ to $\omega\times 2 + 56$. Thus this interval is not $\omega^2$-mlarge.

@@

Let us try another computation.
\input{movies/snippets/Large_Sets_Examples/gnawEx2}

@@

For instance, we can verify that the interval $[6,510]$ is $\omega^2$-mlarge.

@@

\begin{todo}
 Check if the functions $L_\alpha$ are the same as
\cite{KS81}' functions $f\_alpha$ (p. 297).
\end{todo}

@@

Our exploration of the $L_\alpha$\,s  follows the usual scheme : transfinite induction, and proof-by-cases : zero, successors and limit ordinals.

@@

Useful abstract properties of arithmetic functions are
defined 
in~\href{../theories/html/hydras.Prelude.Iterates.html\#fun_le}{Prelude.Iterates}.

\label{sect:abstract-arith-prop}

\input{movies/snippets/Iterates/funLeDef}

We prove also that the functions we consider are strictly monotonous. The section on successor ordinals has the following structure.

@@

\input{movies/snippets/Large_Sets/phi0Mult}

@@

\input{movies/snippets/L_alpha/Paraphrases}

@@

By  well-founded induction on $\alpha$, we prove the following lemmas:

@@

@@

\index{hydras}{Projects}
\begin{project}
Instead of considering standard paths and battles, consider ``constant'' paths and the corresponding battles. Please use \texttt{Equations} in order to define the function that computes the length of the $k$-path which leads  from $\alpha$ to $0$.
Prove a few  exact formulas and minoration lemmas.
\end{project}

@@

\input{movies/snippets/Hprime/paraphrases}

@@

\input{movies/snippets/Hprime/HprimeExamples}

@@

It looks hard to capture the complexity of this function by looking only at this
``exact'' formula. 
Let us consider a simple example: the number $H'_{\omega^3}(3)$.

@@

Now, we have got at last an exact formula for $H'_{\omega^\omega}$.

@@

In \coq{}, we follow the  proof in~\cite{KS81}. This proof is mainly a single  proof by transfinite induction on $\alpha$ of the conjunction of the five properties.
For each $\alpha$, the three cases : $\alpha=0$, $\alpha$ is a limit, and 
$\alpha$ is a successor are considered. Inside each case, the five sub-properties are proved sequentially, using the abstract properties defined in Sect~\vref{sect:abstract-arith-prop}

@@

% By elimination, we get a catalogue of properties of the functions $L'_\alpha$:

% \begin{Coqsrc}
% Section Abstract_Properties.
%  Variable alpha : E0.

%  Theorem H'_alpha_mono : strict_mono (H'_ alpha).

%  Theorem H'_alpha_gt : alpha <> Zero ->
%         forall n, n < H'_ alpha n.

%  Theorem H'_alpha_Succ_le :
%         H'_ alpha <<= H'_ (Succ alpha).

%  Theorem H'_alpha_dom :
%     dominates_from 1 (H'_ (Succ alpha)) (H'_ alpha).

%  Theorem H'_restricted_mono_l :
%     forall beta n, Canon_plus n alpha beta -> 
%                                  H'_ beta n <= H'_ alpha n.

%   Lemma H'_alpha_ge_id : id <<= H'_ alpha.

%   Lemma H'_alpha_mono_weak : forall k l, k <= l ->
%                                         H'_ alpha k <= H'_ alpha l.

% End Abstract_Properties.
% \end{Coqsrc}

Using a few lemmas \emph{à la} Ketonen-Solovay, we prove that
if $\alpha<\beta$, then $H'_\beta$ eventually dominates
$H'_\alpha$.
We let the reader look at its proof (Section \texttt{Proof\_of\_H'\_mono\_l} of \href{../theories/html/hydras.Epsilon0.Hprime.html\#H_}{Epsilon0.Hprime}).

@@

Ketonen and Solovay introduce in~\cite{KS81} a ``trivial'' variant of the Wainer hierarchy~\cite{BW85, Wainer1970} of fast growing functions, indexed by ordinals below $\epsilon_0$.

@@

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_\alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$. A module about 
the classic Wainer hierarchy is in preparation.
\end{remark}

A first attempt is to write a definition of $F_\alpha$ by equations, in the same way as for $H\_alpha$.  We use the functional \texttt{iterate} defined in 
Module~\href{../theories/html/hydras.Prelude.Iterates.html\#iterate}{Prelude.Iterates}.

@@

The following code comes from 
 \href{../theories/html/hydras.Epsilon0.F_alpha.html}{Epsilon0.F\_alpha}.

@@

\input{movies/snippets/F_alpha/goodDef}

It is quite easy to prove that our function \texttt{F\_} satisfies the equations on page~\pageref{sect:F-equations}.
\index{hydras}{Library Prelude!iterate}

@@

As a corollary, we prove the following proposition, p. 284 of~\cite{KS81}.
\begin{quote}
  If $\beta<\alpha$, $F_\alpha$ dominates $F_\beta$.
\end{quote}

@@

\section{Conclusion}

@@

%%% TODO : Check the statement !
%
% \index{hydras}{Exercises}
% \begin{exercise}
% Let us quote a theorem from ~\cite{KS81} (page 297).

% \begin{quote}
% \begin{align*}
%   H'_{\omega^\alpha}(n+1) &\geq F_{\alpha}(n) \quad (n\geq 1, \alpha<\epsilon_0) \\
%  F_{\alpha}(n+1) &\geq H'_{\omega^\alpha}(n) \quad (n\geq 1, \alpha<\epsilon_0) 
% \end{align*}
% Thus $H'_{\omega^\alpha}$ and $F_{\alpha}$ have essentially the same order of growth.

% \end{quote}

%  But, before trying to prove these facts, look at the definition of function $H$ in Ketonen and Solovay's paper ! Is it really the same as the definition we quote from Pr{\H o}mel's chapter~\cite{Promel2013},
% whereas \cite{KS81} define $H_\alpha(n)$ as ``the least integer $k$ such that $[n,k]$ is $\alpha$-large''. Thus, it may be useful to adapt the statement above.

%  \subsection{Gnawing ordinals}

% \begin{definition}[After~\cite{KS81}]
%   Let $S$ be a finite set of positive integers, and $\alpha$ be an ordinal strictly less than $\epsilon_0$.  Let us denote by $s=s_1,s_2, \dots, s_N$ the sequence of 
% the elements of $S$, enumerated in strictly increasing order.

% We consider the sequence of ordinals $\alpha_o=\alpha, \alpha_1=\canonseq{\alpha_0}{s_1},\dots,\alpha_{i+1}=\canonseq{\alpha_i}{s_{i+1}},\dots, 
% \alpha_{N}=\canonseq{\alpha_{N-1}}{s_N}$.
% We denote by $\gnaw{s}{\alpha}$ the last ordinal of the sequence, \emph{i.e.}  $\alpha_N$.
% \end{definition}

% The following function computes $\gnaw{s}{\alpha}$ by recursion on $s$.
% \vspace{4pt}

% For instance, let us consider the ordinal $\omega^\omega$, and try some sequence of integers.

% \begin{Coqsrc}
% Compute pp (gnaw (omega ^ omega) (1::nil)).  
% \end{Coqsrc}

% \begin{Coqanswer}
%   = omega%pT1 : ppT1
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute pp (gnaw (omega ^ omega) (1::2::nil)).  
% \end{Coqsrc}

% \begin{Coqanswer}
% = P_fin 2
%      : ppT1
% \end{Coqanswer}

% Likewise, we can verify that $\gnaw{\omega^\omega}{\langle 1,2,3 \rangle}=1$
% and $\gnaw{\omega^\omega}{\langle 1,2,3,4 \rangle}=0$.

% \begin{Coqsrc}
% Example omega_omega_1_4 : gnaw (omega ^omega) (interval 1 4) = 0.
% Proof. trivial. Qed.

% Example omega_omega_1_3 : gnaw (omega ^omega) (interval 1 3) = 1.
% Proof. trivial. Qed.
% \end{Coqsrc}

% \begin{remark}
% \label{remark:gnaw-vs-battles}
% Let us consider an hydra battle, where Hercules always chops off the rightmost head of the hydra. Let $\alpha<\epsilon_0$ be an ordinal number, and 
% $s=\langle i_1<i_2<\dots<i_N\rangle$ be  any finite sequence of positive integers.
% Then the battle initiated by the hydra $\iota(\alpha)$, with $s$ as the sequence of successive replication factors, leads to the hydra $\iota(\gnaw{s}{\alpha})$ as the final state.
% \end{remark}

% \subsection{Large sequences}

% \begin{remark}
% In their article~\cite{KS81}, Ketonen and Solovay use the appellation ``large set'' instead of ``large sequence'', but their definitions use an enumeration of the elements in increasing order. Thus, we shall use the term ``sequence'' when referring to our implementation in \coq{}, and ``set'' when referring to the statements of~\cite{KS81}.
% \end{remark}

% \begin{definition}[After\cite{KS81}]
% The sequence $s$ is said to be \emph{$\alpha$-large} if $\gnaw{\alpha}{s}=0$.  
% \end{definition}

% \begin{Coqsrc}
% Definition largeb (alpha : T1) (s: list nat) :=
%   match gnaw alpha s with
%     | zero => true
%     | _ => false
%   end.

% Definition large (alpha : T1) (s : list nat) : Prop :=
%   largeb alpha s.
% \end{Coqsrc}

% For instance, the sequence $\langle 1,2,3,4 \rangle$ is $\omega^\omega$-large but not
% $\omega^{\omega+1}$-large, since $\gnaw{\omega^{\omega+1}}{\langle 1,2,3,4\rangle}$ is equal to $\omega \times 2 + 4$.

% %\omega^\omega+\omega^2\times 3 + \omega\times 4+ 5$.

% \begin{Coqsrc}
% Compute largeb (omega^omega) (interval 1 4).  
% \end{Coqsrc}

% \begin{Coqanswer}
% = true : bool
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute largeb (omega^(omega+1)) (interval 1 4).
% \end{Coqsrc}

% \begin{Coqanswer}
% = false : bool
% \end{Coqanswer}

% \begin{remark}
% A sequence $s$ is $\alpha$-large if (still considering Hercules ``righmost-head'', tactic), it leads to Hercules' victory.
% \end{remark}

% \subsection{A little game}

% Let $\alpha<\epsilon_0$ be an ordinal, and $i$ a positive integer. We want to guess the least natural number  $j$  such that the interval $[i,i+j]$ is $\alpha$-large.
% Equivalently, we should have $\gnaw{\alpha}{[i, i+j-1]}=1$.

% The following functions takes three arguments: an ordinal $\alpha$, and two positive natural numbers  $i$ and $j$ (we assume, but not verify that $i$ and $j$ are strictly positive). It returns one of the three possible answers:

% \begin{itemize}
% \item \texttt{Ok} if $j$ is the smallest integer such that the interval $[i,i+j]$ is $\alpha$-large
% \item \texttt{Too\_far} if $[i,i+j]$ is  $\alpha$-large, but $j$ is not the smallest such positive integer
% \item \texttt{(Remaining $\beta$)} if $j$ is too small, and gnawing $\alpha$ with
%   $[i,i+j]$ is still equal to $\beta$, instead of $0$
% \end{itemize}

% \vspace{4pt}
% \noindent
% \emph{From Module~\href{../theories/html/hydras.Epsilon0.Large_Sets_Demo.html}{Ordinals.Epsilon0.Large\_Sets\_Demo}}

% \begin{Coqsrc}
% Inductive answer : Set := You_won | Too_far | Remaining (rest : ppT1).

% Definition large_set_check alpha i j :=
%   let beta := gnaw alpha (interval i (Nat.pred j))
%   in match beta with
%      | one => Ok
%      | zero => Too_far
%      |  _ => Remaining (pp (canonseq j beta))
%      end.
% \end{Coqsrc}

% \subsubsection{\texorpdfstring{$\omega$}{omega}-large intervals}

% For instance, let us consider the ordinal $\omega$ and start with $i=1$.

% \begin{Coqsrc}
% Compute large_set_check omega 1 2.
% \end{Coqsrc}

% \begin{Coqanswer}
%      = Ok
%      : answer
% \end{Coqanswer}

% Let us give greater values of $i$, still with the ordinal $\omega$.

% \begin{Coqsrc}
% Compute large_set_check omega 2 3.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Remaining 1
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check omega 3 3.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Remaining 3
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check omega 2 4.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Ok
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check omega 3 6.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Ok
%      : answer
% \end{Coqanswer}

% It looks like every request to compute (\texttt{large\_set\_check omega $i$ $2\times i$})  will succeed. Let us try an example.

% \begin{Coqsrc}
% Compute large_set_check omega 49 98.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Ok
%      : answer
% \end{Coqanswer}

% \subsubsection{\texorpdfstring{$\omega^2$}{omega\^{}2}-large intervals}

% Still using \texttt{Compute} and \texttt{large\_set\_check}, we obtained the 
% following values of $j$, the least integer such that the interval $[i,j]$ is $\omega^2$ large.

% $$
% \begin{array}{|c|c|}
% \hline
%   i & j \\
% \hline 
% 1 & 4 \\
% 2 & 14 \\
% 3 & 38 \\
% 4 & 94 \\
% 5 & 222 \\
% % 6 & 510 
% \hline
% \end{array}
% $$

% \begin{exercise}
% Please give the 6-th and 7-th line of the array above.
% \end{exercise}

% \subsubsection{The limits of (pure) computation}

% Let us now play with bigger ordinals, for instance $\alpha=\omega^\omega$ or
% $\alpha=\omega^{\omega + 1}$. We notice that, even for small values of $i$, it is hard
% to guess values of $j$ such that $[i,i+j]$ is $\alpha$-large.

% \begin{Coqsrc}
% Compute large_set_check (omega ^ omega) 1 4.
% \end{Coqsrc}

% \begin{Coqanswer}
%  = Ok
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ omega) 2 38.
% \end{Coqsrc}

% \begin{Coqanswer}
%  = Ok
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ omega) 3 1000.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Remaining (omega ^ 2 * 2 + omega * 220 + 798)%pT1
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ omega) 3 1798.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Remaining (omega ^ 2 * 2 + omega * 220)%pT1
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ omega) 3 5000.
% \end{Coqsrc}

% \begin{Coqanswer}
%   = Remaining (omega ^ 2 * 2 + omega * 218 + 2198)%pT1
%      : answer
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ (omega + 1)) 3 5000.
% \end{Coqsrc}

% \begin{Coqanswer}
%  = Remaining
%          (omega ^ omega * 2 + omega ^ 3 * 4 + 
%           omega ^ 2 * 4 + omega * 1148 +  4222)%pT1
%      : answer  
% \end{Coqanswer}

% \begin{Coqsrc}
% Compute large_set_check (omega ^ (omega + 1)) 3 10000.
% \end{Coqsrc}

% \begin{Coqanswer}
% Warning: To avoid stack overflow, large numbers in nat are interpreted as
% applications of Init.Nat.of_uint. [abstract-large-number,numbers]

%     = Remaining
%          (omega ^ omega * 2 + omega ^ 3 * 4 + 
%           omega ^ 2 * 4 + omega * 1147 +
%           8446)%pT1
%      : answer
% \end{Coqanswer}

% Since computation is not enough, let us comme back to proofs, or, better, proofs \emph{and} computations.

% \subsection{Proving largeness}

% %%% ICI %%%

% \subsection{$n$-large and $\omega$-large intervals }

% A finite ordinal is just made out of \texttt{zero} and \texttt{succ} constructions.
% Thus any sequence of strictly positive integers of length greater than  or equal to $n$ will completely gnaw the ordinal $n$.

% Concerning the first limit ordinal $\omega$ the largeness of a sequence $s$ depends only on its first element and the length of the rest of the sequence (please keep in mind that the argument $i$ of $\canonseq{\alpha}{i}$ is meaningful only if $\alpha$ is a limit ordinal).
% The following proposition is labeled $4.2$ in~\cite{KS81}.

% \begin{proposition}
%   For $n<\omega$, a set $X$id $n$-large if and only if $|X|\geq n$.
% A finite set $X$ is $\omega$-large if $|X|>\min{X}$.
% \end{proposition}

% Rewritten in terms of list of strictly positive integers, we get the following statements:

% \begin{Coqsrc}
% Lemma large_n_iff : forall s (n:nat) , ~ In 0 s  ->
%                                   large n s  <-> (n <= List.length s)%nat.
% \end{Coqsrc}

% \begin{Coqsrc}
% Lemma large_omega_iff : forall s n,  ~In 0 (n::s) -> 
%                                             large omega (n::s) <->
%                                             (n <=  List.length s)%nat.
% \end{Coqsrc}

% % \begin{Coqsrc}
% % (* sorted list of natural numbers greater than or equal to n *)

% % Inductive sorted_ge (n: nat) : list nat -> Prop :=
% % | sorted_ge_nil : sorted_ge n nil
% % | sorted_ge_one : forall p, n<=p ->
% %                             sorted_ge n (p::nil)
% % | sorted_ge_cons: forall p q s,  n<=p -> p<q ->
% %                                  sorted_ge p (q::s) ->
% %                                  sorted_ge n (p::q::s).
% % \end{Coqsrc}

% \subsection{Mimimal large sequences}

% Let us consider \emph{minimal} large sequences, \emph{i.e.} large sequences 
% the strict prefix of which do not lead to $0$. In other words, only the last ordinal 
% defined by the sequence is null.  For this purpose, we use the predicate \texttt{path\_to} introduced page~\pageref{path-to-definition}.

% \begin{Coqsrc}
% Definition mlarge alpha s := path_to zero s alpha.
% \end{Coqsrc}

%------------------------------------------------------
\section{A certified catalogue of rapidly growing functions}

In this section, we try to present an abstract of the properties of the main variants of fast-growing hierarchies of functions
we found in the literature or we had to define as helpers in our proofs.

\subsection{Ketonen-Solovay's \texttt{F\_alpha}}

  This hierarchy is presented p.280 of~\cite{KS81} as `` a trivial variant of one introduced by Wainer ''.
  Let us recall the equations shown in Sect.~\vref{F_equations}.

\begin{itemize}
\item $F_0(i)=i+1$
\item $F_{\beta+1}(i)= (F_\beta)^{(i+1)}(i)$, where $f^{(i)}$ is the $i$-th iterate of $f$.
\item $F_\alpha(i) = F_{\canonseq{\alpha}{i}} (i)$ if $\alpha$ is a limit ordinal.
\end{itemize}

Note that \cite{KS81} defines also $F_{\epsilon_0}$ (by the third equation). Since $\epsilon_0$ is not representable in type \texttt{E0}, our translation in \coq{} does not take $F_{\epsilon_0}$ into account.

Several properties of $F_\alpha$ are already presented in Sect.~\ref{F_equations}.

>>>>

\subsection{Examples}

For instance the interval $[6,70]$ leads $\omega^2$ to $\omega\times 2 + 56$. Thus this interval is not $\omega^2$-large.

@@

The interval $[6,700]$ is $\omega^2$-large, but not
$\omega^2$-mlarge, since $[6,699]$ is also $\omega^2$-large.

\input{movies/snippets/Large_Sets_Examples/gnawEx2}

@@

For instance, we prove that the interval $[6,510]$ is $\omega^2$-mlarge.

@@

\begin{todo}
 Check if the functions $L_\alpha$ are the same as
\cite{KS81}' functions $f_\alpha$ (p. 297).
\end{todo}

@@

The properties we consider are defined in \href{../theories/html/hydras.Prelude.Iterates.html\#fun_le}{Prelude.Iterates}.

\label{sect:abstract-arith-prop}
\input{movies/snippets/Iterates/funLeDef}

Our exploration of the $L_\alpha$\,s  considers the usual cases of a proof by transfinite induction: zero, successors and limit ordinals. The lemmas we are going to proved will be applied in a big proof by induction in Sect~\vref{sect:L-correct-proof}.

@@

@@

\inputsnippets{Large_Sets/phi0Mult, Large_Sets/phi0MultOk,
Large_Sets/Phi0MultSLe}

@@

\inputsnippets{L_alpha/Paraphrasesa}
\inputsnippets{L_alpha/Paraphrasesb}
\inputsnippets{L_alpha/Paraphrasesc}

@@

By  well-founded induction on $\alpha$, we prove the following properties:

@@

\label{sect:L-correct-proof}

@@

\index{hydras}{Exercises}
\begin{exercise}
Instead of considering standard paths and battles, consider battles where the replication factor is a constant $k$. Please use \texttt{Equations} in order to define the function that computes the length of the $k$-path which leads  from $\alpha$ to $0$.
Prove a few  exact formulas and minoration lemmas.
\end{exercise}

@@

\input{movies/snippets/Hprime/paraphrasesa}
\input{movies/snippets/Hprime/paraphrasesb}
\input{movies/snippets/Hprime/paraphrasesc}
\input{movies/snippets/Hprime/paraphrasesd}

@@

\input{movies/snippets/Hprime/HprimeExamplesa}
\input{movies/snippets/Hprime/HprimeExamplesb}
\input{movies/snippets/Hprime/HprimeExamplesc}
\input{movies/snippets/Hprime/HprimeExamplesd}

@@

It is hard to capture the complexity of this function by looking only at this
``exact'' formula. 
Let us consider a simple example: the number $H'_{\omega^3}(3)$.

@@

\subsubsection{A formula for \texorpdfstring{$H'_{\omega^\omega}$}{\texttt{H'(phi0(omega))}}}

Now, we can get at last an exact formula for $H'_{\omega^\omega}$.

@@

In \coq{}, we follow the  proof of~\cite{KS81}. This proof is mainly a single  proof by transfinite induction on $\alpha$ of the conjunction of the five properties.
For each $\alpha$, the three cases : $\alpha=0$, $\alpha$ is a limit, and 
$\alpha$ is a successor are considered. Inside each case, the five sub-properties are proved sequentially, using the abstract properties defined in Sect~\vref{sect:abstract-arith-prop}

@@

Using a few lemmas \emph{à la} Ketonen-Solovay, we prove that
if $\alpha<\beta$, then $H'_\beta$ eventually dominates
$H'_\alpha$.
We let the reader look at the proof (Section \texttt{Proof\_of\_H'\_mono\_l} of \href{../theories/html/hydras.Epsilon0.Hprime.html\#H_}{Epsilon0.Hprime}).

@@

Ketonen and Solovay introduce in~\cite{KS81} a ``trivial'' variant of the Wainer hierarchy~\cite{BW85, Wainer1970} of fast growing functions, indexed by ordinals below $\epsilon_0$.
The functions $F_\alpha$ are defined by the following equations.

@@

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_\alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$.

A module about 
the classic Wainer hierarchy is in preparation.

Note also that \cite{KS81} defines also $F_{\epsilon_0}$ (by the third equation). Since $\epsilon_0$ is not representable in type \texttt{E0}, our implementation in \coq{} does not take $F_{\epsilon_0}$ into account.

A first attempt is to write a definition of $F_\alpha$ by equations, in the same way as for $H\_alpha$ (the functional \texttt{iterate} has already been used in Sect.\vref{Functions:iterate}).

@@

\emph{From\href{../theories/html/hydras.Epsilon0.F_alpha.html}{Epsilon0.F\_alpha}~}.

@@

\input{movies/snippets/F_alpha/goodDefa}
\input{movies/snippets/F_alpha/goodDefb}

It is quite easy to prove that our functional \texttt{F\_} satisfies the equations on page~\pageref{sect:F-equations}.
\index{hydras}{Library Prelude!iterate}

@@

As a corollary, we prove that, if $\beta<\alpha$, then
$F_\alpha$ dominates $F_\beta$ (p. 284 of~\cite{KS81}).

@@

\section{More about rapidly growing functions}

@@
